---
title: "viz_part_01"
author: "Ayako Sekiya"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Let's import data
```{r}
library(tidyverse)
library(ggridges)
```

This code from the course website gets the data from specific file in NOAA. 

```{r import}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Let's make a sctterplot
`aes` allows you to assign variables to x and y axis. `geom_point` allows you to add points to the scatterplot.

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))+
geom_point()
```

Let's make the scatterplot a bit different. 
added `drop_na` to remove na and remove error. 
`filter` allows to chose specific outputs

```{r}
weather_df %>%
  drop_na() %>%
  filter(name=="CentralPark_NY") %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

Let's make the same scatterplot a bit different. 

```{r}
weather_scatterplot=
  weather_df %>%
  drop_na() %>%
  ggplot(aes(x = tmin, y = tmax))

weather_scatterplot+
  geom_point()
```

## Let's fancy this up a bit!

We add color to distinguish which plot is which using `color`. 

```{r color}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))
```

```{r line}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) +
  geom_smooth(se = FALSE)
```

the following adds lines to every plot.

```{r line}
ggplot(weather_df, aes(x = tmin, y = tmax, color=name)) + 
  geom_point() +
  geom_smooth()
```

gives transparent circles and `se` can be set to false to remove wanrings. 

```{r line}
ggplot(weather_df, aes(x = tmin, y = tmax, color=name)) + 
  geom_point(alpha=0.3) +
  geom_smooth(se= FALSE)
```

make separate panels with `facet_grid`.

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

this reorganizes to show rows. 

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(name ~ .)
```

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = .3) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

## some quick stuff

weather_df %>%
  mutate(farenheit= INSERT CONVERSION HERE)

```{r hexagons}
ggplot(weather_df, aes(x = date, y = tmax1)) + 
  geom_hex() 
```

## univariate plots...

Histograms, densityplots, boxplots, violins...

```{r histogram}
ggplot(weather_df, aes(x = tmax)) + 
  geom_histogram()
```

`fill` what do you fill bars with?
`dodge` allows you to unoverlap

```{r colors}
ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_histogram(position = "dodge", binwidth = 2)
```

Density plots!

```{r density plots}
ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_density(alpha = .3, adjust = .5, color = "blue")
```

Boxplots!

```{r boxplots}
ggplot(weather_df, aes(x = name, y = tmax, fill=name))+ 
  geom_boxplot()
```

Violin plots!--> good with comparing 20,30 stations, when have fewer plots to compare. 

```{r violinplots}
ggplot(weather_df, aes(x = name, y = tmax)) + 
  geom_violin(aes(fill = name), alpha = .5) + 
  stat_summary(fun = "median", color = "blue")
```

Ridgeplots!

```{r ridgeplots}
ggplot(weather_df, aes(x = tmax, y = name)) + 
  geom_density_ridges(scale = .85)
```

## saving and editing files

```{r}
weather_scatterplot=
  weather_df %>%
  ggplot(aes(x=date, y=tmax, color= name)) +
  geom_point(aes(size= prcp), alpha=0.3)+
  geom_smooth(se=FALSE)+
  facet_grid(. ~ name)

ggsave("results/weather_scatterplot.pdf", weather_plot, width = 8, height = 5)
```


```{r}
weather_plot = ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) 

ggsave("results/weather_plot.pdf", weather_plot, width = 8, height = 5)
```

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))
```

